High geomagnetic field intensity recorded by anorthosite xenoliths requires a vigorous late Mesoproterozoic geodynamo

### 2022-04-07 PNAS_manuscript/Supporting Info.tex

\begin{figure*}[h!]
\noindent\includegraphics[width=17.8 cm]{PINT_BiCEP.pdf}
\centering
\caption{{Violin plots of site-level posterior paleointensity distributions estimated using the bias corrected estimation of paleointensity (BiCEP) method developed by \citealp{Cych2021a}. Blue bars of each violin plot represents the median of the distributions. The yellow dashed line is the mean paleointensity of the posterior estimates across all sites. Assuming that paleointensity estimates from specimens that come from a same cooling unit are distributed around a true paleointensity value with the various deflections being expressed as the curvature parameter of the NRM/TRM plot \cite{Arai1963a, Paterson2011a}, the method uses all paleointensity measurement-level data without applying selection criteria. For comparison of results from this independent method with those based on our selection (as show in Fig. 4 in manuscript), we highlight the anorthosite sites that pass our paleointensity selection and make other anorthosite and diabase transparent. The results from the BiCEP method address the uncertainties associated with anorthosite AX6 and AX8. This is associated with the relatively variable specimen behaviors within these two sites. But for sites AX10, AX11, AX13, AX12, and AX16, the posterior probability distributions have very narrow bounds, consistent with the interpretation that these anorthosites are faithful paleointensity recorders that have high-quality paleointensity behaviors. AX-anorthosite xenolith site; BD-Beaver River diabase site. The grouping of cooling unit is based on the spacial proximity between site locations and the inclusion relationship of host diabase and anorthosite xenoliths reported by \citealp{Zhang2021b}.}}
\label{fig:PINT_BiCEP}
\end{figure*}

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth]{MPMS.pdf}
\centering
\caption{{Low-temperature magnetic property measurement system (MPMS) experiment results. ``Pass" or ``Fail" represents whether their sister specimens passed our paleointensity selection or not. In the field-cooled (FC) experiments, the magnetization was measured upon warming following the specimen having cooled in an applied field of 2.5 T from 300 to 10 K. In the zero-field-cooled (ZFC) experiment, a low-temperature saturation isothermal remanence (LTSIRM) of 2.5 T was applied at 10 K after the specimen cooled in a (near-)zero field. In the room-temperature saturation isothermal remanence (RTSIRM) experiment, the sample was pulsed with a 2.5 T field at room temperature ($\sim$300 K) and then cooled to 10 K and warmed back to room temperature in a (near-) zero field. Specimen AX6-1r is from anorthosite AX6 which passed our paleointensity selection. It has a well-defined Verwey transition $\sim$120 K \cite{Verwey1939a}. Specimens AX3-2r-ni and BD2-2r show Verwey transition but the transition temperatures are suppressed below $\sim$120 K. Specimen BD2-2r has a consistently higher moment during the zero-field-cooled step than during the field-cooled step. This is consistent with the interpretation that multidomian magnetic carriers exist in significant quantity in this specimen \cite{Carter-Stiglitz2006a}.}}
\label{fig:MPMS}
\end{figure}

@@

\begin{figure*}[h!]
\noindent\includegraphics[width=17.8 cm]{Cooling_rate_correction.pdf}
\centering
\caption{{Graph of predicted paleointensity overestimate due to slow cooling of the intrusive Beaver River diabase and anorthosite xenoliths relative to the cooling rate in laboratory following the model of \citealp{Halgedahl1980a}. Because the majority of the anorthosites have unblocking temperatures between 500\textdegree C and 580\textdegree C, we estimate that the slow cooling during natural remanence acquisition could have resulted in a 36\% overestimate. Thus, a correction factor of 0.74 is applied at specimen level for the paleointensity summary plot.}}
\label{fig:PINT_cooling_corrected}
\end{figure*}

@@

\begin{figure*}[h!]
\noindent\includegraphics[width=0.9\textwidth]{Cenozoic_resample_SI.pdf}
\centering
\caption{\footnotesize{A) Summary plot of individual specimen absolute paleointensity results (square symbols) and their averages and standard deviations at site level (black bars with grey uncertainty boxes) from this study. All results are corrected for cooling rate with a factor of 0.74. Each `AX' site is an individual anorthosite xenolith within the Beaver River diabase. The sites with successful experiments come from 3 regions which would have cooled at distinct times yielding similar estimates within the each region with differences between regions. B) Specimen level means calculated for these regions are compared to the distribution of intensities calculated from the existing paleointensity data in the PINT database (PINT v8.0.0; \url{http://www.pintdb.org/}; \citealp{Bono2021a}) at the latitude corresponding to the paleolatitude of study region (22\textdegree N). C) The mean of the 3 regional means is compared to means calculated from 3 random values drawn from the Cenozoic data. The paleointensity records used for resampling are filtered for Q$_{PI} \geq$3 \cite{Biggin2014a}. The distribution represents a total of 10,000 iterations of taking 3 random draws and calculating the mean.}}
\label{fig:Cenozoic_PINT}
\end{figure*}

@@

\begin{figure*}[h!]
\noindent\includegraphics[width=0.9\textwidth]{example_unmix_plot_with_data.pdf}
\centering
\caption{\footnotesize{A) Example coercivity spectra of anorthosite and diabase specimens from sites that pass or fail our paleointensity selection criteria. The specimens and fits are the same as those shown in Figure 5 in the manuscript. Data points used for fitting the coercivity curves are shown in this figure. }}
\label{fig:Cenozoic_PINT}
\end{figure*}

@@

\caption{\footnotesize{Specimen paleointensity results that passed our selection. Paleointensity results for specimens that passed quality criteria. B$_{anc}$ is the calculated ancient field intensity over the chosen temperature interval in $\mu$T. T$_{min}$ and T$_{max}$ indicate the temperature interval over which the best fit for paleointensity was defined. N is the number of steps used within the selected interval for paleointensity determination. FRAC is the fraction of remanence. NpTRM shows the number of pTRM checks within the selected interval for paleointensity determination. $\beta$ is the scatter parameter.  GAP-MAX is the maximum magnetization gap between two adjacent steps. MAD is the maximum angle of deviation. DANG is the deviation angle. SCAT is the scatter parameter. Paleolatitude is calculated from the inclination values reported in \cite{Zhang2021b}. $\gamma$ is the gamma statistic that measures the angle between the last pTRM step used for paleointensity determination and the applied field direction. V(A)DM is the virtual (axial) dipole moment reported in $10^{21}$Am$^2$ (ZAm$^2$). }}

@@

\begin{tabular}{cccccccccccccccc}

@@

Site & Specimen & B$_{anc}$ & T$_{min}$ & T$_{max}$ & N    & FRAC & NpTRM & $\beta$ & GAP-MAX & MAD ($^\circ$) & DANG ($^\circ$) & SCAT & Paleolatitude & $\gamma$ & VADM (ZAm$^2$) \\

@@

AX6  & AX6-2a   & 18.25     & 400       & 585       & 18 & 0.7  & 10    & 0.04    & 0.12    & 3.44           & 3.43            & PASS & 21.97         & 2.7      & 29.34         \\
AX6  & AX6-3a   & 25.39     & 400       & 585       & 18 & 0.76 & 10    & 0.04    & 0.1     & 4.28           & 2.88            & PASS & 21.97         & 3.2      & 40.82         \\
AX6  & AX6-1a   & 47.36     & 475       & 585       & 15 & 0.6  & 10    & 0.02    & 0.16    & 2.92           & 1.67            & PASS & 21.97         & 2        & 76.13         \\
AX8  & AX8-3a   & 41.3      & 400       & 580       & 17 & 0.75 & 9     & 0.03    & 0.14    & 4.38           & 2.22            & PASS & 22.98         & 11.2     & 65.53         \\
AX8  & AX8-2a   & 50.51     & 400       & 580       & 17 & 0.63 & 9     & 0.04    & 0.16    & 3.19           & 1.29            & PASS & 22.98         & 3.7      & 80.15         \\
AX8  & AX8-1a   & 65.38     & 425       & 566       & 13 & 0.6  & 8     & 0.07    & 0.2     & 5.28           & 2.95            & PASS & 22.98         & 7        & 103.74        \\
AX10 & AX10-1a  & 45.84     & 425       & 585       & 17 & 0.78 & 10    & 0.06    & 0.24    & 5.6            & 2.62            & PASS & 20.37         & 4.7      & 75.2          \\
AX10 & AX10-2a  & 46.61     & 450       & 585       & 16 & 0.62 & 10    & 0.04    & 0.2     & 5.32           & 2.24            & PASS & 20.37         & 7.8      & 76.46         \\
AX10 & AX10-3a  & 48.01     & 425       & 585       & 17 & 0.69 & 10    & 0.04    & 0.24    & 4.02           & 1.56            & PASS & 20.37         & 5.8      & 78.76         \\
AX11 & AX11-1a  & 73.29     & 425       & 560       & 10 & 0.67 & 6     & 0.08    & 0.21    & 5.28           & 2.54            & PASS & 19.43         & 5.9      & 121.64        \\
AX11 & AX11-2a  & 73.29     & 400       & 560       & 11 & 0.65 & 6     & 0.07    & 0.21    & 3.94           & 1.51            & PASS & 19.43         & 9.9      & 121.64        \\
AX11 & AX11-4a  & 73.31     & 500       & 570       & 11 & 0.66 & 8     & 0.09    & 0.2     & 1.53           & 3.27            & PASS & 19.43         & 5.6      & 121.68        \\
AX11 & AX11-6a  & 73.32     & 200       & 562       & 14 & 0.69 & 7     & 0.07    & 0.17    & 4              & 1.33            & PASS & 19.43         & 3        & 121.69        \\
AX11 & AX11-9a  & 73.34     & 100       & 562       & 15 & 0.67 & 7     & 0.06    & 0.17    & 5.34           & 1.13            & PASS & 19.43         & 11.9     & 121.73        \\
AX11 & AX11-3a  & 73.41     & 400       & 560       & 11 & 0.66 & 6     & 0.08    & 0.21    & 3.95           & 2.11            & PASS & 19.43         & 8.2      & 121.84        \\
AX11 & AX11-5a  & 73.44     & 400       & 566       & 14 & 0.73 & 8     & 0.05    & 0.18    & 2.93           & 0.85            & PASS & 19.43         & 1.9      & 121.89        \\
AX12 & AX12-14a & 30.34     & 475       & 585       & 16 & 0.75 & 10    & 0.06    & 0.17    & 1.74           & 0.55            & PASS & 35.73         & 0.9      & 40.86         \\
AX12 & AX12-1a  & 33.89     & 0         & 580       & 21 & 0.97 & 9     & 0.03    & 0.17    & 5.47           & 4.73            & PASS & 35.73         & 10       & 45.64         \\
AX12 & AX12-6a  & 37.18     & 425       & 564       & 12 & 0.69 & 7     & 0.08    & 0.22    & 3.64           & 2.05            & PASS & 35.73         & 5        & 50.07         \\
AX12 & AX12-8a  & 38.34     & 475       & 565       & 12 & 0.75 & 8     & 0.06    & 0.25    & 1.46           & 2.29            & PASS & 35.73         & 1.6      & 51.63         \\
AX12 & AX12-4a  & 41.89     & 500       & 585       & 14 & 0.66 & 10    & 0.05    & 0.24    & 3.85           & 3.19            & PASS & 35.73         & 11.4     & 56.42         \\
AX12 & AX12-2a  & 46.94     & 425       & 570       & 14 & 0.7  & 8     & 0.05    & 0.24    & 3.39           & 2.38            & PASS & 35.73         & 7        & 63.22         \\
AX13 & AX13-3a  & 71.68     & 100       & 550       & 12 & 0.71 & 5     & 0.08    & 0.22    & 5.92           & 1.88            & PASS & 19.36         & 3.4      & 119.07        \\
AX13 & AX13-7a  & 72.6      & 475       & 585       & 15 & 0.61 & 10    & 0.03    & 0.2     & 3.62           & 2.09            & PASS & 19.36         & 11.6     & 120.6         \\
AX13 & AX13-4a  & 76.13     & 200       & 550       & 11 & 0.65 & 5     & 0.04    & 0.18    & 8.82           & 1.07            & PASS & 19.36         & 3.7      & 126.47        \\
AX13 & AX13-6a  & 76.8      & 200       & 555       & 12 & 0.7  & 6     & 0.06    & 0.22    & 3.82           & 1.53            & PASS & 19.36         & 4.5      & 127.58        \\
AX13 & AX13-2a  & 76.86     & 200       & 555       & 12 & 0.71 & 6     & 0.05    & 0.2     & 8.08           & 2.23            & PASS & 19.36         & 4.1      & 127.68        \\
AX13 & AX13-9a  & 77.48     & 0         & 564       & 17 & 0.94 & 7     & 0.03    & 0.16    & 5.96           & 1.07            & PASS & 19.36         & 2.6      & 128.71        \\
AX13 & AX13-8a  & 84.83     & 450       & 570       & 13 & 0.81 & 8     & 0.02    & 0.24    & 3.69           & 1.82            & PASS & 19.36         & 5.1      & 140.92        \\
AX16 & AX16-15a & 31.91     & 475       & 570       & 13 & 0.61 & 8     & 0.07    & 0.17    & 3.07           & 1.41            & PASS & 30.08         & 2.6      & 46.16         \\
AX16 & AX16-13a & 41.68     & 400       & 570       & 15 & 0.72 & 8     & 0.07    & 0.2     & 3.47           & 1.85            & PASS & 30.08         & 1.1      & 60.29         \\
AX16 & AX16-16a & 43.3      & 400       & 562       & 13 & 0.65 & 7     & 0.09    & 0.18    & 5.14           & 2.94            & PASS & 30.08         & 2        & 62.63         \\
AX16 & AX16-14a & 43.64     & 400       & 565       & 14 & 0.63 & 8     & 0.08    & 0.14    & 3.84           & 2.12            & PASS & 30.08         & 6        & 63.13         \\
AX16 & AX16-11a & 44.17     & 450       & 570       & 14 & 0.7  & 8     & 0.06    & 0.15    & 2.86           & 2.07            & PASS & 30.08         & 4.6      & 63.89         \\
AX16 & AX16-4a  & 44.82     & 425       & 575       & 15 & 0.76 & 9     & 0.05    & 0.21    & 4.77           & 1.08            & PASS & 30.08         & 4.2      & 64.83         \\
AX16 & AX16-1a  & 44.9      & 200       & 564       & 15 & 0.87 & 7     & 0.06    & 0.22    & 5.56           & 2.4             & PASS & 30.08         & 4.5      & 64.95         \\
AX16 & AX16-5a  & 44.91     & 425       & 560       & 10 & 0.65 & 6     & 0.1     & 0.24    & 7.42           & 3.9             & PASS & 30.08         & 4        & 64.96         \\
AX16 & AX16-2a  & 45.05     & 425       & 564       & 12 & 0.65 & 7     & 0.07    & 0.22    & 4.25           & 1.44            & PASS & 30.08         & 4.9      & 65.17         \\
AX16 & AX16-9a  & 48.04     & 500       & 585       & 15 & 0.61 & 10    & 0.04    & 0.17    & 2.98           & 1.23            & PASS & 30.08         & 4.3      & 69.49         \\
AX16 & AX16-10a & 53.27     & 510       & 585       & 14 & 0.62 & 10    & 0.04    & 0.2     & 2.75           & 1.1             & PASS & 30.08         & 5.5      & 77.06          \\

>>>>

\begin{figure*}[h!]
\noindent\includegraphics[width=17.8 cm]{PINT_BiCEP.pdf}
\centering
\caption{{Violin plots of site-level posterior paleointensity distributions estimated using the bias corrected estimation of paleointensity (BiCEP) method developed by ref. \citealp{Cych2021a}. Blue bars of each violin plot represent the median of the distributions. The yellow dashed line is the mean paleointensity of the posterior estimates across all sites estimated using BiCEP (38.82 $\pm$ 4.60 mT). Assuming that paleointensity estimates from specimens that come from a same cooling unit are distributed around a true paleointensity value with the various deflections being expressed as the curvature parameter of the NRM/TRM plot \cite{Arai1963a, Paterson2011a}, the method uses all paleointensity measurement-level data without applying selection criteria. For comparison of results from this independent method with those based on our selection (as show in Fig. 4 in manuscript), we highlight the anorthosite sites that pass our paleointensity selection and make other anorthosite and diabase more transparent. The results from the BiCEP method address the uncertainties associated with anorthosite AX6 and AX8. This is associated with the relatively variable specimen behaviors within these two sites. For sites AX10, AX11, AX13, AX12, and AX16, the posterior probability distributions have very narrow bounds, consistent with the interpretation that these anorthosites are faithful paleointensity recorders that have high-quality paleointensity behaviors. AX--anorthosite xenolith site; BD--Beaver River diabase site. The grouping of cooling units is based on the spatial proximity between site locations and the inclusion relationship of host diabase and anorthosite xenoliths reported by ref. \citealp{Zhang2021b}.}}
\label{fig:PINT_BiCEP}
\end{figure*}

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth]{MPMS.pdf}
\centering
\caption{{Low-temperature magnetic property measurement system (MPMS) experiment results. ``Pass" or ``Fail" represents whether their sister specimens passed our paleointensity selection or not. In the field-cooled (FC) experiments, the magnetization was measured upon warming following the specimen having cooled in an applied field of 2.5 T from 300 to 10 K. In the zero-field-cooled (ZFC) experiment, a low-temperature saturation isothermal remanence (LTSIRM) of 2.5 T was applied at 10 K after the specimen cooled in a (near-)zero field. In the room-temperature saturation isothermal remanence (RTSIRM) experiment, the sample was pulsed with a 2.5 T field at room temperature ($\sim$300 K) and then cooled to 10 K and warmed back to room temperature in a (near-) zero field. Specimen AX6-1r is from anorthosite AX6 which passed our paleointensity selection. It has a well-defined Verwey transition $\sim$120 K \cite{Verwey1939a}. Specimens AX3-2r-ni and BD2-2r show Verwey transition but the transition temperatures are suppressed below $\sim$120 K. Specimen BD2-2r has a consistently higher moment during the zero-field-cooled step than during the field-cooled step. This is consistent with the interpretation that multidomain (MD) magnetic carriers exist in significant quantity in this specimen \cite{Carter-Stiglitz2006a}.}}
\label{fig:MPMS}
\end{figure}

@@

\begin{figure*}[h!]
\noindent\includegraphics[width=17.8 cm]{Cooling_rate_correction.pdf}
\centering
\caption{{Graph of predicted paleointensity overestimate due to slow cooling of the intrusive Beaver River diabase and anorthosite xenoliths relative to the cooling rate in laboratory following the model of \citealp{Halgedahl1980a}. Because the majority of the anorthosites have unblocking temperatures between 500\textdegree C and 580\textdegree C, we estimate that the slow cooling during natural remanence acquisition could have resulted in a 33\% overestimate. Thus, a correction factor of 0.75 is applied at specimen level for the paleointensity summary plot.}}
\label{fig:PINT_cooling_corrected}
\end{figure*}

@@

\begin{figure*}[h!]
\noindent\includegraphics[width=0.9\textwidth]{Cenozoic_resample_SI.pdf}
\centering
\caption{\footnotesize{Data from this study as in Figure 4 of the main text, but compared to the Cenozoic paleointensity database rather than the PADM2M model. A) Summary plot of individual specimen absolute paleointensity results (square symbols) and their averages and standard deviations at site level (black bars with grey uncertainty boxes) from this study. All results are corrected for cooling rate with a factor of 0.75. Each `AX' site is an individual anorthosite xenolith within the Beaver River diabase. The sites with successful experiments come from 3 regions which would have cooled at distinct times yielding similar estimates within the each region with differences between regions. B) Specimen level means calculated for these regions are compared to the distribution of intensities calculated from the existing paleointensity data in the Cenozoic (past 66 Myr) in the PINT database (PINT v8.0.0; \url{http://www.pintdb.org/}; \citealp{Bono2021a}) at the latitude corresponding to the paleolatitude of study region (22\textdegree N). C) The mean of the 3 regional means is compared to means calculated from 3 random values drawn from the Cenozoic data. The paleointensity records used for resampling are filtered for Q$_{PI} \geq$3 \cite{Biggin2014a}. The distribution represents a total of 10,000 iterations of taking 3 random draws and calculating the mean.}}
\label{fig:Cenozoic_PINT}
\end{figure*}

@@

\begin{figure*}[h!]
\noindent\includegraphics[width=0.9\textwidth]{example_unmix_plot_with_data.pdf}
\centering
\caption{\footnotesize{Example coercivity spectra of anorthosite and diabase specimens from sites that pass or fail our paleointensity selection criteria. The specimens and fits are the same as those shown in Figure 5 in the manuscript. Data points used for fitting the coercivity curves are shown in this figure. }}
\label{fig:Cenozoic_PINT}
\end{figure*}

@@

\caption{\footnotesize{Specimen paleointensity results that passed our selection. B$_{anc}$ is the calculated ancient field intensity over the chosen temperature interval in $\mu$T. T$_{min}$ and T$_{max}$ indicate the temperature interval over which the best fit for paleointensity was defined. N is the number of steps used within the selected interval for paleointensity determination. FRAC is the fraction of remanence used for fitting. NpTRM shows the number of pTRM checks within the selected interval for paleointensity determination. $\beta$ is the scatter parameter. GAP-MAX is the maximum magnetization gap between two adjacent steps. MAD is the maximum angle of deviation. DANG is the deviation angle. SCAT is the scatter parameter. inc$_{tc}$ is the tilt-corrected inclination. Paleolatitude is calculated from the inclination values reported in \cite{Zhang2021b}. $\gamma$ is the gamma statistic that measures the angle between the last pTRM step used for paleointensity determination and the applied field direction. V(A)DM is the virtual (axial) dipole moment reported in $10^{21}$Am$^2$ (ZAm$^2$). }}

@@

\begin{tabular}{ccccccccccccccccc}

@@

Site & Specimen & B$_{anc}$ & T$_{min}$ & T$_{max}$ & N  & FRAC & NpTRM & $\beta$ & GAP-MAX & MAD ($^\circ$) & DANG ($^\circ$) & SCAT & inc$_{tc}$ & Paleolatitude & $\gamma$ & VDM (ZAm$^2$) \\

@@

AX6  & AX6-2a   & 13.72     & 400       & 585       & 18 & 0.70 & 10    & 0.04    & 0.12    & 3.4            & 3.4             & PASS & 38.9       & 22.0          & 2.7      & 29.8          \\
AX6  & AX6-3a   & 19.09     & 400       & 585       & 18 & 0.76 & 10    & 0.04    & 0.10    & 4.3            & 2.9             & PASS & 38.9       & 22.0          & 3.2      & 41.4          \\
AX6  & AX6-1a   & 35.61     & 475       & 585       & 15 & 0.60 & 10    & 0.02    & 0.16    & 2.9            & 1.7             & PASS & 38.9       & 22.0          & 2.0      & 77.3          \\
AX8  & AX8-3a   & 31.05     & 400       & 580       & 17 & 0.75 & 9     & 0.03    & 0.14    & 4.4            & 2.2             & PASS & 40.3       & 23.0          & 11.2     & 66.5          \\
AX8  & AX8-2a   & 37.98     & 400       & 580       & 17 & 0.63 & 9     & 0.04    & 0.16    & 3.2            & 1.3             & PASS & 40.3       & 23.0          & 3.7      & 81.4          \\
AX8  & AX8-1a   & 49.16     & 425       & 566       & 13 & 0.60 & 8     & 0.07    & 0.20    & 5.3            & 3.0             & PASS & 40.3       & 23.0          & 7.0      & 105.3         \\
AX10 & AX10-1a  & 34.47     & 425       & 585       & 17 & 0.78 & 10    & 0.06    & 0.24    & 5.6            & 2.6             & PASS & 36.6       & 20.4          & 4.7      & 76.3          \\
AX10 & AX10-2a  & 35.05     & 450       & 585       & 16 & 0.62 & 10    & 0.04    & 0.20    & 5.3            & 2.2             & PASS & 36.6       & 20.4          & 7.8      & 77.6          \\
AX10 & AX10-3a  & 36.10     & 425       & 585       & 17 & 0.69 & 10    & 0.04    & 0.24    & 4.0            & 1.6             & PASS & 36.6       & 20.4          & 5.8      & 79.9          \\
AX11 & AX11-1a  & 55.11     & 425       & 560       & 10 & 0.67 & 6     & 0.08    & 0.21    & 5.3            & 2.5             & PASS & 35.2       & 19.4          & 5.9      & 123.5         \\
AX11 & AX11-2a  & 55.11     & 400       & 560       & 11 & 0.65 & 6     & 0.07    & 0.21    & 3.9            & 1.5             & PASS & 35.2       & 19.4          & 9.9      & 123.5         \\
AX11 & AX11-4a  & 55.12     & 500       & 570       & 11 & 0.66 & 8     & 0.09    & 0.20    & 1.5            & 3.3             & PASS & 35.2       & 19.4          & 5.6      & 123.5         \\
AX11 & AX11-6a  & 55.13     & 200       & 562       & 14 & 0.69 & 7     & 0.07    & 0.17    & 4.0            & 1.3             & PASS & 35.2       & 19.4          & 3.0      & 123.5         \\
AX11 & AX11-9a  & 55.14     & 100       & 562       & 15 & 0.67 & 7     & 0.06    & 0.17    & 5.3            & 1.1             & PASS & 35.2       & 19.4          & 11.9     & 123.5         \\
AX11 & AX11-3a  & 55.20     & 400       & 560       & 11 & 0.66 & 6     & 0.08    & 0.21    & 4.0            & 2.1             & PASS & 35.2       & 19.4          & 8.2      & 123.7         \\
AX11 & AX11-5a  & 55.22     & 400       & 566       & 14 & 0.73 & 8     & 0.05    & 0.18    & 2.9            & 0.9             & PASS & 35.2       & 19.4          & 1.9      & 123.7         \\
AX12 & AX12-14a & 22.81     & 475       & 585       & 16 & 0.75 & 10    & 0.06    & 0.17    & 1.7            & 0.6             & PASS & 55.2       & 35.7          & 0.9      & 41.5          \\
AX12 & AX12-1a  & 25.48     & 0         & 580       & 21 & 0.97 & 9     & 0.03    & 0.17    & 5.5            & 4.7             & PASS & 55.2       & 35.7          & 10.0     & 46.3          \\
AX12 & AX12-6a  & 27.95     & 425       & 564       & 12 & 0.69 & 7     & 0.08    & 0.22    & 3.6            & 2.1             & PASS & 55.2       & 35.7          & 5.0      & 50.8          \\
AX12 & AX12-8a  & 28.83     & 475       & 565       & 12 & 0.75 & 8     & 0.06    & 0.25    & 1.5            & 2.3             & PASS & 55.2       & 35.7          & 1.6      & 52.4          \\
AX12 & AX12-4a  & 31.50     & 500       & 585       & 14 & 0.66 & 10    & 0.05    & 0.24    & 3.9            & 3.2             & PASS & 55.2       & 35.7          & 11.4     & 57.3          \\
AX12 & AX12-2a  & 35.29     & 425       & 570       & 14 & 0.70 & 8     & 0.05    & 0.24    & 3.4            & 2.4             & PASS & 55.2       & 35.7          & 7.0      & 64.2          \\
AX13 & AX13-3a  & 53.89     & 100       & 550       & 12 & 0.71 & 5     & 0.08    & 0.22    & 5.9            & 1.9             & PASS & 35.1       & 19.4          & 3.4      & 120.9         \\
AX13 & AX13-7a  & 54.59     & 475       & 585       & 15 & 0.61 & 10    & 0.03    & 0.20    & 3.6            & 2.1             & PASS & 35.1       & 19.4          & 11.6     & 122.4         \\
AX13 & AX13-4a  & 57.24     & 200       & 550       & 11 & 0.65 & 5     & 0.04    & 0.18    & 8.8            & 1.1             & PASS & 35.1       & 19.4          & 3.7      & 128.4         \\
AX13 & AX13-6a  & 57.74     & 200       & 555       & 12 & 0.70 & 6     & 0.06    & 0.22    & 3.8            & 1.5             & PASS & 35.1       & 19.4          & 4.5      & 129.5         \\
AX13 & AX13-2a  & 57.79     & 200       & 555       & 12 & 0.71 & 6     & 0.05    & 0.20    & 8.1            & 2.2             & PASS & 35.1       & 19.4          & 4.1      & 129.6         \\
AX13 & AX13-9a  & 58.26     & 0         & 564       & 17 & 0.94 & 7     & 0.03    & 0.16    & 6.0            & 1.1             & PASS & 35.1       & 19.4          & 2.6      & 130.7         \\
AX13 & AX13-8a  & 63.78     & 450       & 570       & 13 & 0.81 & 8     & 0.02    & 0.24    & 3.7            & 1.8             & PASS & 35.1       & 19.4          & 5.1      & 143.0         \\
AX16 & AX16-15a & 23.99     & 475       & 570       & 13 & 0.61 & 8     & 0.07    & 0.17    & 3.1            & 1.4             & PASS & 49.2       & 30.1          & 2.6      & 46.8          \\
AX16 & AX16-13a & 31.34     & 400       & 570       & 15 & 0.72 & 8     & 0.07    & 0.20    & 3.5            & 1.9             & PASS & 49.2       & 30.1          & 1.1      & 61.2          \\
AX16 & AX16-16a & 32.56     & 400       & 562       & 13 & 0.65 & 7     & 0.09    & 0.18    & 5.1            & 2.9             & PASS & 49.2       & 30.1          & 2.0      & 63.6          \\
AX16 & AX16-14a & 32.81     & 400       & 565       & 14 & 0.63 & 8     & 0.08    & 0.14    & 3.8            & 2.1             & PASS & 49.2       & 30.1          & 6.0      & 64.1          \\
AX16 & AX16-11a & 33.21     & 450       & 570       & 14 & 0.70 & 8     & 0.06    & 0.15    & 2.9            & 2.1             & PASS & 49.2       & 30.1          & 4.6      & 64.9          \\
AX16 & AX16-4a  & 33.70     & 425       & 575       & 15 & 0.76 & 9     & 0.05    & 0.21    & 4.8            & 1.1             & PASS & 49.2       & 30.1          & 4.2      & 65.8          \\
AX16 & AX16-1a  & 33.76     & 200       & 564       & 15 & 0.87 & 7     & 0.06    & 0.22    & 5.6            & 2.4             & PASS & 49.2       & 30.1          & 4.5      & 65.9          \\
AX16 & AX16-5a  & 33.77     & 425       & 560       & 10 & 0.65 & 6     & 0.10    & 0.24    & 7.4            & 3.9             & PASS & 49.2       & 30.1          & 4.0      & 65.9          \\
AX16 & AX16-2a  & 33.87     & 425       & 564       & 12 & 0.65 & 7     & 0.07    & 0.22    & 4.3            & 1.4             & PASS & 49.2       & 30.1          & 4.9      & 66.1          \\
AX16 & AX16-9a  & 36.12     & 500       & 585       & 15 & 0.61 & 10    & 0.04    & 0.17    & 3.0            & 1.2             & PASS & 49.2       & 30.1          & 4.3      & 70.5          \\
AX16 & AX16-10a & 40.05     & 510       & 585       & 14 & 0.62 & 10    & 0.04    & 0.20    & 2.8            & 1.1             & PASS & 49.2       & 30.1          & 5.5      & 78.2         \\
